### 2023-04-10 chapter2/chapter2.tex
Added hierarchy figure

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy.png}
\centering
\caption{\textbf{Hierarchical clustering of evolutionary signatures.}
The AIC difference between the Brownian motion (BM) and Ornstein-Uhlenbeck (OU) models is measure of their relative goodness of fit to the data with a penalty for the number of parameters in each. Larger values indicate a better fit by the OU model.}
\label{fig:hierarchy}
\end{figure}
